Reconstructing Propositional Proofs in Type Theory

### 2017-11-21 paper/sections/metis-language-and-proofs.tex
[ paper ] fixed some typos related with nnf.

The \TPTP language is the input language to encode problems used by \Metis.
It includes the first-order form (denoted by \name{fof}) and clause normal form (denoted by \name{cnf}) formats~\cite{sutcliffe2009}.
The \TPTP syntax\footnote{See the complete grammar
at \url{http://www.cs.miami.edu/~tptp/TPTP/SyntaxBNF.html}} describes a well-defined grammar to handle annotated
formulas with the following form:

>>>>

The \TPTP language is the input language to encode problems used by \Metis.
It includes the first-order form (denoted by \name{fof}) and clause normal form (denoted by \name{cnf}) formats~\cite{sutcliffe2009}.
The \TPTP syntax\footnote{See the complete syntax grammar
at \url{http://www.cs.miami.edu/~tptp/TPTP/SyntaxBNF.html}} describes a well-defined grammar to handle annotated
formulas with the following form:

### 2017-11-21 paper/sections/proof-reconstruction.tex
[ paper ] fixed some typos related with nnf.

\begin{equation*}
  \begin{aligned}
  &\hspace{.495mm}\fun{metisRule} : \Source → \Target → \Prop\\
  &\begin{array}{ll}
  \fun{metisRule}~φ~ψ\ &=
      \begin{cases}
      ψ, &\text{if the conclusion}ψ\text{ can be}\text{ derived by applying certain inference}\\
         &\text{rules to the premise }φ;\\
      φ, &\text{otherwise;}
      \end{cases}
  \end{array}
  \end{aligned}
\end{equation*}

@@

% -----------------------------------------------------------------------------

@@

%------------------------------------------------------------------------------

>>>>

\begin{equation*}
  \begin{aligned}
  &\hspace{.495mm}\fun{metisRule} : \Source → \Target → \Prop\\
  &\begin{array}{ll}
  \fun{metisRule}~φ~ψ\ &=
      \begin{cases}
      ψ, &\text{if the conclusion }ψ\text{ can be}\text{ derived by applying certain inference}\\
         &\text{rules to the premise }φ;\\
      φ, &\text{otherwise;}
      \end{cases}
  \end{array}
  \end{aligned}
\end{equation*}

@@

% ------------------------------------------------------------------

@@

% -------------------------------------------------------------------

### 2017-11-21 paper/sections/proof-reconstruction/resolve.tex
[ paper ] fixed some typos related with nnf.

\begin{mainlemma}
  \label{lem:reorder-and}
  If $Γ ⊢ φ$ and $ψ : \Target$ then $Γ ⊢ \freorder_{∧}~φ~ψ$, where
    \begin{align}
      \begin{split}
      \label{eq:reorder-and}
        &\freorder_{∧} : \Source \to \Target \to \Prop\\
        &\freorder_{∧}~φ~ψ =
        \begin{cases}
          φ, &\text{ if }φ ≡ ψ;\\
          ψ₁ ∧ ψ₂, &\text{ if } ψ ≡ ψ₁ ∧ ψ₂\text{, }ψ₁ ≡ \freorder_{∧}~φ~ψ₁;\\
                   &\text{ and } ψ₂ ≡ \freorder_{∧}~φ~ψ₂;\\
          φ,       &\text{ if } ψ ≡ ψ₁ ∧ ψ₂\\
          \fconjunct~φ~ψ, &\text{ otherwise.}
        \end{cases}
      \end{split}
  \end{align}
\end{mainlemma}

@@

\begin{myexamplenum}\hspace{10cm}
\label{ex:resolve-tstp}
\begin{verbatim}
  cnf(r₄, (¬ r ∨ p ∨ q), ...
  cnf(r₅, (p ∨ q ∨ r), ...
  cnf(r₆, (p ∨ q), inf(resolve, r, [r₅, r₄])).
\end{verbatim}

@@

If the scenario would have other like replacing \verb!r₅! by
\begin{verbatim}
  cnf(r₅, (r ∨ p ∨ q), ...
\end{verbatim}
The \resolve rule have could derive $(p ∨ q) ∨ (p ∨ q)$, but again, that is not the expected result.
\end{myexamplenum}

>>>>

\begin{mainlemma}
  \label{lem:reorder-and}
  If $Γ ⊢ φ$ and $ψ : \Target$ then $Γ ⊢ \freorder_{∧}~φ~ψ$, where
    \begin{align}
      \begin{split}
      \label{eq:reorder-and}
        &\freorder_{∧} : \Source \to \Target \to \Prop\\
        &\freorder_{∧}~φ~ψ =
        \begin{cases}
          φ, &\text{ if }φ ≡ ψ;\\
          ψ₁ ∧ ψ₂, &\text{ if } ψ ≡ ψ₁ ∧ ψ₂\text{, }ψ₁ ≡ \freorder_{∧}~φ~ψ₁;\\
                   &\text{ and } ψ₂ ≡ \freorder_{∧}~φ~ψ₂;\\
          φ,       &\text{ if } ψ ≡ ψ₁ ∧ ψ₂;\\
          \fconjunct~φ~ψ, &\text{ otherwise.}
        \end{cases}
      \end{split}
  \end{align}
\end{mainlemma}

@@

\begin{myexamplenum}\hspace{10cm}
\label{ex:resolve-tstp}
\begin{verbatim}
  cnf(r₄, ¬ r ∨ p ∨ q, ...
  cnf(r₅, p ∨ q ∨ r, ...
  cnf(r₆, p ∨ q, inf(resolve, r, [r₅, r₄])).
\end{verbatim}

@@

If the scenario would have other like replacing \verb!r₅! by
\begin{verbatim}
  cnf(r₅, r ∨ p ∨ q, ...
\end{verbatim}
The \resolve rule have could derive $(p ∨ q) ∨ (p ∨ q)$, but again, that is not the expected result.
\end{myexamplenum}
